### 2014-06-06 method.tex
typo

Most ROIs that go through the CNN in R-CNN do not contain objects of interest, and are simply background.
It would be useful to quickly reject these regions, without expending the full amount of computation on them. Since most of the time is spend in the convolution layers, we introduce a reject layer after layer 1, 2, and 3, this allows skipping the computation of the following convolutions. These reject layers were trained using the corresponding fine-tuned CNN.

>>>>

Most ROIs that go through the CNN in R-CNN do not contain objects of interest, and are simply background.
It would be useful to quickly reject these regions, without expending the full amount of computation on them. Since most of the time is spent in the convolution layers, we introduce a reject layer after layer 1, 2, and 3, this allows skipping the computation of the following convolutions. These reject layers were trained using the corresponding fine-tuned CNN.
